\documentclass{ximera}

\title{Introduction}
\author{Bart Snapp}

\begin{document}
\begin{abstract}
    What is Ximera?
\end{abstract}
\maketitle

Ximera, pronounced ``chimera,'' (\textbf{X}imera: \textbf{I}nteractive,
\textbf{M}athematics, \textbf{E}ducation,
\textbf{R}esources, for \textbf{A}ll) is an open-source platform that provides
tools for
authoring and publishing (PDF and Online), open-source, interactive educational
content, such as textbooks, assessments, and online courses.

\paragraph{Authors}  write and store their content on their own
machines and GitHub repositories.
Authors own their content and decide how to license their content. From a
single source written in \LaTeX, Ximera generates various output: PDF
worksheets,
PDF textbooks, and	PDF solution manuals, and so on. Of most interest,
Ximera can
also create online interactive activities:
\begin{center}
    \begin{tikzpicture}
        % {\resizebox{1cm}{!}{\input{document.tex}}};   %%% FIX WITH PIC TECHNOLOGY
        \node at (-1.8,.2) {\small PDF};
        % \node at (-2,0) {\resizebox{1cm}{!}{\input{document.tex}}};    %%% FIX WITH PIC TECHNOLOGY
        \node at (-2,0) {\small PDF};
        
        % \node at (-2.2,-.2){\resizebox{1cm}{!}{\input{document.tex}}};    %%% FIX WITH PIC TECHNOLOGY
        \node at (-2.2,-.2) {\small PDF};
        \draw[->] (-.6,0) -- (-1.3,0);
        \draw[->] (-.6,.3) -- (-1.3,.3);
        \draw[->] (-.6,-.3) -- (-1.3,-.3);

        % \node at (0,0) {\resizebox{1cm}{!}{\input{document.tex}}};    %%% FIX WITH PIC TECHNOLOGY
        \node at (0,0) {\LaTeX};
        \draw[->] (.6,0) -- (1.4,0);

        \node at (2,0) {\resizebox{1cm}{!}{\input{server.tex}}};
        \draw[->] (2.6,0) -- (3.4,0);
        % \node at (4,0) {\resizebox{1cm}{!}{\input{computer.tex}}};     %%% FIX WITH PIC TECHNOLOGY
        
        \node[anchor=north] at (-2,-.8) {Various};
        \node[anchor=north] at (-2,-1.2) {PDFs};

        \node[anchor=north] at (0,-.8) {Single};
        \node[anchor=north] at (0,-1.2) {Source};

        \node[anchor=north] at (2,-.8) {Deploy};
        \node[anchor=north] at (2,-1.2) {Server};

        \node[anchor=north] at (4,-.8) {Students};
        \node[anchor=north] at (4,-1.2) {Engage};

    \end{tikzpicture}
\end{center}
The source code used to produce PDFs can also create interactive online
activities when deployed to a Ximera server. Students access this content via a
URL or an assignment in their LMS.

\paragraph{Get involved} by contributing as an instructor, author,
or developer. To get started with Ximera, visit our
\textit{First Steps in Ximera} GitHub repository:
\begin{center}
    \qrcode{https://go.osu.edu/xfs}\\
    \small\url{https://go.osu.edu/xfs}
\end{center}
\textbf{This document assumes you have completed the instructions there, and
    have
    successively deployed Ximera content online.}

\paragraph{Funding for the Ximera Project} is provided by
a U.S.\ Department of Education Open Textbooks Pilot Program grant in the
amount of \$2,125,000, from 2024--2026, with no external funding.
In the past, the Ximera Project has
also received support from NSF Grant DUE-1245433, the Shuttleworth
Foundation, the Ohio State University
Department of Mathematics, and the Affordable Learning Exchange at OSU.

As a token of our appreciation, \textbf{consider applying for a Ximera
    Flash-Grant Stipend:}
\begin{center}
    \qrcode{https://go.osu.edu/ximera-flash-grant}\\
    \small\url{https://go.osu.edu/ximera-flash-grant}
\end{center}
Thank you for your interest in Ximera. We encourage you to contact the
team with any questions you may have.

\paragraph{The authors} listed on the cover are the current Ximera lead
developers. In reality, this document has many authors as it is part of an
evolution of Ximera documentation. Rodney Austin, Oscar Levin, Matt Thomas, and Hans
Parshall authored parts of the either the document class or original
documentation.

In particular, we should mention the contributions of Claire Merriman, who worked to reshape much of our
previous content into this current User Manual.
\end{document}