\documentclass{ximera}

\title{Printing with style}

\author{Bart Snapp}

\begin{document}
\begin{abstract}
We describe methods of styling the print versions of Ximera materials.
\end{abstract}
\maketitle
 


\section{Documentclass options}

There are a number of options for the document class, though their
effects are only seen in the PDF:
 
%% Copied from dtx
\begin{description}
\item[\tt\bfseries handout] The default behavior of the class is to display \textbf{all} content. This means that if any questions are asked, all answers are shown. Moreover, some content will only have a meaningful presentation when displayed online. When compiled without any options, this content will be shown too. This option will supress such content and generate a reasonable printiable ``handout.''
\item[\tt\bfseries noauthor] By default, authors are listed at the bottom of the first page of a document. This option will supress the listing of the authors.
\item[\tt\bfseries nooutcomes] By default, learning outcomes are listed at the bottom of the first page of a document. This option will supress the listing of the learning outcomes.
\item[\tt\bfseries instructornotes] This option will turn on (and off) notes written for the instructor.
\item[\tt\bfseries noinstructornotes] This option will turn off (and on) notes written for the instructor.
\item[\tt\bfseries hints] When the \texttt{handout} options is used, hints are not shown. This option will make hints visible in handout mode.
\item[\tt\bfseries newpage] This option will start each problem-like environment (\texttt{exercise}, \texttt{question}, \texttt{problem}, and \texttt{exploration}) start on a new page.
\item[\tt\bfseries numbers] This option will number the titles of the activity. By default the activities are unnumbered.
\item[\tt\bfseries wordchoicegiven] This option will replace the choices shown by \texttt{wordChoice} with the correct choice. No indication of the \texttt{wordChoice} environment will be shown.
\end{description}


GIVE EXAMPLES OF COMBOS OF THESE AND WHAT THEY DO

\section{The preamble versus printing styles}

The preamble is used to make the Ximera document compile.

The printing style is used to make cosmetic changes to the PDF.



\section{When and how to use \texttt{prompt}}



\end{document}